---
title: "RT_Disengagement_raw_output"
output: html_document
date: "2026-04-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 Ceci Westbrook, 2026
 This is a subsection of analysis code for the purpose of demonstrating raw output. Some important functions 
 (e.g., file readin) are removed to maintain data anonymity.

```{r include = FALSE}
library(dplyr)
library(reshape2)
library(lme4)
library(lmerTest)
library(ggplot2)
library(tidyverse)

dest_vol <- file.path("/Users/westbrook/OneDrive - UPMC/Documents/Hallion/PT disengagement/behav_analyses")
load(file.path(dest_vol,"TReWBehavDataAll.Rdata"))
```

After reading in our data, let's make a composite dyscontrol score
Q3_1 = repetitive; Q3_2 = intrusive; Q3_3 = uncontrollable

```{r}
alldata$dyscontrol <- rowMeans(alldata[,c("Q3_1","Q3_2","Q3_3")],na.rm=T)
```

now let's make the imputed score where NAs are replaced with zeros
```{r}
alldata$Q3_1_imputed <- ifelse(is.na(alldata$Q3_1),0,alldata$Q3_1)
alldata$Q3_2_imputed <- ifelse(is.na(alldata$Q3_2),0,alldata$Q3_2)
alldata$Q3_3_imputed <- ifelse(is.na(alldata$Q3_3),0,alldata$Q3_3)
alldata$dyscontrol_imputed <- rowMeans(alldata[,c("Q3_1_imputed","Q3_2_imputed","Q3_3_imputed")],na.rm=T)
```

## Analyses
### Pre-scan dyscontrol ratings

Skill index (note: this was inaccurately called 'accuracy index' at first)  
Imputed scores:

```{r warning = FALSE}
m1 <- lmer(scale(dyscontrol_imputed) ~ scale(AccIndex) + (1 + AccIndex|participant), data = alldata)
summary(m1)
confint(m1)
```
Raw scores - effect is the same:
```
m1 <- lmer(scale(dyscontrol) ~ scale(AccIndex) + (1 + AccIndex|participant), data = alldata)
summary(m1)
confint(m1)
```

```
plotting
```{r warning = FALSE}
g <- ggplot(alldata,aes(x=dyscontrol,y=AccIndex))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol,AccIndex), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="Pre-scan Dyscontrol Rating") +
  scale_y_continuous(name="SART Skill Index")
```

checking for influential outlier: model remains significant
```{r warning = FALSE}
m1 <- lmer(scale(dyscontrol_imputed) ~ scale(AccIndex) + (1 + AccIndex|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)
```

## looking at speed/accuracy differences:  
## Accuracy  
linear model is significant--but not for imputed values
```{r warning = FALSE}
m1 <- lm(dyscontrol ~ NoGo_ACC, data = alldata)
summary(m1)

m1 <- lm(dyscontrol_imputed ~ NoGo_ACC, data = alldata)
summary(m1)
```
MLM is NOT significant for either
```{r warning = FALSE}
m1 <- lmer(scale(dyscontrol_imputed) ~ scale(NoGo_ACC) + (1+NoGo_ACC|participant), data = alldata)
summary(m1)
confint(m1)

m1 <- lmer(scale(dyscontrol) ~ scale(NoGo_ACC) + (1+NoGo_ACC|participant), data = alldata)
summary(m1)
confint(m1)
```

plotting
```{r warning = FALSE}
g <- ggplot(alldata,aes(x=dyscontrol_imputed,y=NoGo_ACC))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol_imputed,NoGo_ACC), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="Pre-scan Dyscontrol Rating") +
  scale_y_continuous(name="No-Go Accuracy") 
```

## Speed  
linear model is significant
```{r warning = FALSE}
m1 <- lm(dyscontrol_imputed ~ Mean_go_RT, data = alldata)
summary(m1)

m1 <- lm(dyscontrol ~ Mean_go_RT, data = alldata)
summary(m1)
```

multi-level model IS significant
```{r warning = FALSE}
m1 <- lmer(scale(dyscontrol_imputed) ~ scale(Mean_go_RT) + (1 + Mean_go_RT|participant), data = alldata)
summary(m1)
confint(m1)

m1 <- lmer(scale(dyscontrol) ~ scale(Mean_go_RT) + (1 + Mean_go_RT|participant), data = alldata)
summary(m1)
confint(m1)
```
plotting
```{r warning = FALSE}
g <- ggplot(alldata,aes(x=dyscontrol_imputed,y=Mean_go_RT))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol_imputed,Mean_go_RT), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="Pre-scan Dyscontrol Rating\n (repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Mean Go RT") #+ geom_text(label = alldata$participant)
```

and robust to outliers:
```{r warning = FALSE}
meanRTsbysubj <- alldata %>% group_by(participant) %>% summarise(overall_mean_RT = mean(Mean_go_RT,na.rm=T))
meanRTsbysubj[which(meanRTsbysubj$overall_mean_RT > mean(meanRTsbysubj$overall_mean_RT) + 3*sd(meanRTsbysubj$overall_mean_RT)),]

m1 <- lmer(scale(dyscontrol_imputed) ~ scale(Mean_go_RT) + (1 + Mean_go_RT|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)

m1 <- lmer(scale(dyscontrol) ~ scale(Mean_go_RT) + (1 + Mean_go_RT|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)
```
plotting w/o outlier
```{r warning = FALSE}
g <- ggplot(alldata[alldata$participant!=393,],aes(x=dyscontrol_imputed,y=Mean_go_RT))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol_imputed,Mean_go_RT), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="Pre-scan Dyscontrol Rating\n (repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Mean Go RT") 
```

```{r warning = FALSE}
# one big combined plot
g1 <- ggplot(alldata[alldata$participant!=393,],aes(x=dyscontrol_imputed,y=AccIndex)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol_imputed,AccIndex), lwd = 2, alpha = 1) +
  annotate(
    geom = "text",
    x = 5.0,
    y = 2.5,
    label = "*",
    color="red",
    size = 10) +
  theme(legend.position="none") +
  theme(axis.title.x = element_blank()) + theme(axis.title.y = element_text(size=18)) +
  scale_x_continuous(name="Pre-Scan Uncontrollability Rating (How much is this thought repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Skill Index (arbitrary units)") 

g2 <- ggplot(alldata[alldata$participant!=393,],aes(x=dyscontrol_imputed,y=NoGo_ACC)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol_imputed,NoGo_ACC), lwd = 2, alpha = 1) +
  theme(legend.position="none") + theme(axis.title.y = element_text(size=18),axis.title.x = element_text(size=18)) +
  scale_x_continuous(name="Pre-Scan Uncontrollability Rating (How much is this thought repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="No-Go Accuracy (percent correct)") 

g3 <- ggplot(alldata[alldata$participant!=393,],aes(x=dyscontrol_imputed,y=Mean_go_RT)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(dyscontrol_imputed,Mean_go_RT), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  annotate(
    geom = "text",
    x = 5.0,
    y = 1.0,
    label = "†",
    color="red",
    size = 8) +
  theme(axis.title.x = element_blank()) + theme(axis.title.y = element_text(size=18)) +
  scale_x_continuous(name="Pre-Scan Uncontrollability Rating (How much is this thought repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Mean Go RT (s)") 

library(egg)
plot3 <- ggarrange(g1,g2,g3,ncol=3)
```

# Thought probes  
```{r include = FALSE}
alldata$probe1 <- as.numeric(alldata$probe1)
alldata$probe2 <- as.numeric(alldata$probe2)
alldata$probe3 <- as.numeric(alldata$probe3)
alldata$probe4 <- as.numeric(alldata$probe4)
alldata$probe5 <- as.numeric(alldata$probe5)
alldata$probe6 <- as.numeric(alldata$probe6)
```
## Probe 1: End-of-trial dyscontrol (To what extent were your thoughts repetitive, intrusive, or hard to control?")  
  
## Skill index
run only as multilevel models - significant
```{r warning = FALSE}
m1 <- lmer(probe1 ~ AccIndex + (1+AccIndex|participant), data = alldata)
summary(m1)

m1 <- lmer(scale(probe1) ~ scale(AccIndex) + (1+AccIndex|participant), data = alldata)
summary(m1)
confint(m1)
```

adding baseline dyscontrol - still significant!
```{r warning = FALSE}
m1 <- lmer(scale(probe1) ~ scale(AccIndex) + scale(dyscontrol_imputed) + (1+AccIndex|participant), data = alldata)
summary(m1)
confint(m1)

m1 <- lmer(scale(probe1) ~ scale(AccIndex) + (1+AccIndex|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)

m1 <- lmer(scale(probe1) ~ scale(AccIndex) + scale(dyscontrol_imputed) + (1+AccIndex|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)
```

adding task effort - still significant
```{r warning = FALSE}
m1 <- lmer(scale(probe1) ~ scale(AccIndex) + scale(probe3) + (1+AccIndex|participant), data = alldata)
summary(m1)
confint(m1)
```

plotting
```{r warning = FALSE}
g <- ggplot(alldata,aes(x=probe1,y=AccIndex))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,AccIndex), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="End-of-trial Dyscontrol Rating\n (How much were thoughts\nrepetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Accuracy Index") 
```

## Speed/accuracy breakdown  
Speed
```{r warning = FALSE}
m1 <- lmer(scale(probe1) ~ scale(Mean_go_RT) + (1+Mean_go_RT|participant), data = alldata[alldata$Mean_go_RT<1.0,])
summary(m1)
confint(m1)
```
plotting
```{r warning = FALSE}
g <- ggplot(alldata[alldata$Mean_go_RT<1.0,],aes(x=probe1,y=Mean_go_RT))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,Mean_go_RT), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="End-of-trial Dyscontrol Rating\n (How much were thoughts\nrepetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Mean Go RT") 
```

not quite robust to one outlier
```{r warning = FALSE}
m1 <- lmer(scale(probe1) ~ scale(Mean_go_RT) + (1+Mean_go_RT|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)
```
plotting w/o outlier
```{r warning = FALSE}
g <- ggplot(alldata[alldata$participant!=393,],aes(x=probe1,y=Mean_go_RT))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,Mean_go_RT), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="End-of-trial Dyscontrol Rating\n (How much were thoughts\nrepetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Mean Go RT") 
```

not significant if baseline dyscontrol included
```{r warning = FALSE}
m1 <- lmer(scale(probe1) ~ scale(Mean_go_RT) + scale(dyscontrol_imputed) + (1+Mean_go_RT|participant), data = alldata[alldata$Mean_go_RT<1.0,])
summary(m1)
confint(m1)
```

## Accuracy
```{r warning = FALSE}
m1 <- lmer(scale(probe1) ~ scale(NoGo_ACC) + (1+NoGo_ACC|participant), data = alldata)
summary(m1)
confint(m1)

m1 <- lmer(scale(probe1) ~ scale(NoGo_ACC) + (1+NoGo_ACC|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)

m1 <- lmer(scale(probe1) ~ scale(NoGo_ACC) + scale(dyscontrol_imputed) + (1+NoGo_ACC|participant), data = alldata[alldata$participant!=393,])
summary(m1)
confint(m1)
```
plotting
```{r warning = FALSE}
g <- ggplot(alldata[alldata$NoGo_ACC<1.0,],aes(x=probe1,y=NoGo_ACC))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,NoGo_ACC), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="End-of-trial Dyscontrol (repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="No-Go Accuracy") 

g <- ggplot(alldata[alldata$participant!=393,],aes(x=probe1,y=NoGo_ACC))
g + geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,NoGo_ACC), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  scale_x_continuous(name="End-of-trial Dyscontrol (repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="No-Go Accuracy") 
```

one big combined plot
```{r warning = FALSE}
g1 <- ggplot(alldata[alldata$participant!=393,],aes(x=probe1,y=AccIndex)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,AccIndex), lwd = 2, alpha = 1) +
  annotate(
    geom = "text",
    x = 50,
    y = 2.5,
    label = "*",
    color="red",
    size = 10) +
  theme(legend.position="none") +
  theme(axis.title.x = element_blank()) + theme(axis.title.y = element_text(size=18)) +
  scale_x_continuous(name="End-of-trial Uncontrollability (How much were thoughts repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Skill Index (arbitrary units)") 

g2 <- ggplot(alldata[alldata$participant!=393,],aes(x=probe1,y=NoGo_ACC)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,NoGo_ACC), lwd = 2, alpha = 1) +
  theme(legend.position="none") + theme(axis.title.y = element_text(size=18), axis.title.x = element_text(size=18)) +
  scale_x_continuous(name="End-of-trial Uncontrollability (How much were thoughts repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="No-Go Accuracy (percent correct)") 

g3 <- ggplot(alldata[alldata$participant!=393,],aes(x=probe1,y=Mean_go_RT)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe1,Mean_go_RT), lwd = 2, alpha = 1) +
  annotate(
    geom = "text",
    x = 50,
    y = 0.9,
    label = "*",
    color="red",
    size = 10) +
  theme(legend.position="none") +
  theme(axis.title.x = element_blank()) + theme(axis.title.y = element_text(size=18)) +
  scale_x_continuous(name="End-of-trial Uncontrollability (How much were thoughts repetitive, intrusive, or hard to control?)") +
  scale_y_continuous(name="Mean Go RT (s)") 

library(egg)
plot3 <- ggarrange(g1,g2,g3,ncol=3)
```

# Probe 3: Task effort ("To what extent were you trying (making an effort) to focus on the task?")  

Skill index, accuracy and speed

```{r warning = FALSE}
m1 <- lmer(AccIndex ~ probe3 + (1|participant), data = alldata)
summary(m1)

m2 <- lmer(NoGo_ACC ~ probe3 + (1|participant), data = alldata)
summary(m2)

m3 <- lmer(Mean_go_RT ~ probe3 + (1|participant), data = alldata)
summary(m3)
```

Relationship to end-of-trial dyscontrol
```{r warning = FALSE}
m4 <- lmer(probe1 ~ probe3 + (1|participant), data = alldata)
summary(m4)
```
one big combined plot
```{r warning = FALSE}
g1 <- ggplot(alldata,aes(x=probe3,y=AccIndex)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe3,AccIndex), lwd = 2, alpha = 1) +
  annotate(
    geom = "text",
    x = 50,
    y = 2.5,
    label = "*",
    color="red",
    size = 10) +
  theme(legend.position="none") +
  theme(axis.title.x = element_blank()) + theme(axis.title.y = element_text(size=18)) +
  scale_x_continuous(name="End-of-trial Effort (were you trying (making an effort) to focus on the task?)") +
  scale_y_continuous(name="Skill Index (arbitrary units)") 

g2 <- ggplot(alldata,aes(x=probe3,y=NoGo_ACC)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe3,NoGo_ACC), lwd = 2, alpha = 1) +
  theme(legend.position="none") + theme(axis.title.y = element_text(size=18),axis.title.x = element_text(size=18)) +
  scale_x_continuous(name="End-of-trial Effort (were you trying (making an effort) to focus on the task?)") +
  scale_y_continuous(name="No-Go Accuracy (percent correct)") 

g3 <- ggplot(alldata,aes(x=probe3,y=Mean_go_RT)) +
  geom_point(aes(color=as.factor(participant)), alpha = 0.4) +
  geom_line(stat="smooth",method="lm", alpha = 0.4, aes(color = as.factor(participant)), size = 0.5, se = F) +
  geom_smooth(data = alldata, method = "lm", aes(probe3,Mean_go_RT), lwd = 2, alpha = 1) +
  theme(legend.position="none") +
  annotate(
    geom = "text",
    x = 50,
    y = 1.0,
    label = "†",
    color="red",
    size = 8) +
  theme(axis.title.x = element_blank()) + theme(axis.title.y = element_text(size=18)) +
  scale_x_continuous(name="End-of-trial Effort (were you trying (making an effort) to focus on the task?)") +
  scale_y_continuous(name="Mean Go RT (s)") 

library(egg)
plot3 <- ggarrange(g1,g2,g3,ncol=3)
```

# Investigating missing data
```{r include = FALSE}
alldata[,c(1,16:51)]
library(naniar)
```
Check for missingness at random: suggests data are NOT missing completely at random
```{r warning = FALSE}
mcar_test(alldata[,c(16:51)]) # p < .03
```

```{r include = FALSE}
long_df <- alldata[,c(1:2,16:51)] %>%
  pivot_longer(
    cols = starts_with("Q"),
    names_to = "category",
    values_to = "rating"
  )

long_df_model <- long_df %>%
  mutate(
    is_na = is.na(rating),
    is_zero = ifelse(rating == 0, 1, 0)  # this will be NA when rating is NA
  )
long_df_model <- long_df_model %>%
  mutate(is_zero = ifelse(is.na(is_zero), 0, is_zero))

participant_summary <- long_df_model %>%
  group_by(participant) %>%
  summarise(
    mean_rating = mean(rating, na.rm = TRUE),
    na_prop = mean(is_na),
    .groups = "drop"
  )
```

The more NAs, the higher the rating - suggests that there are missing ratings at the bottom of the scale (0s)
```{r warning = FALSE}
cor_test <- cor.test(participant_summary$mean_rating, participant_summary$na_prop)
print(cor_test)
```

plotting
```{r warning = FALSE}
ggplot(participant_summary, aes(x = mean_rating, y = na_prop)) +
  geom_point(alpha = 0.6, color = "tomato") +
  geom_smooth(method = "lm", se = FALSE, color = "steelblue") +
  labs(title = "Proportion of Missing Responses vs. Mean Rating",
       x = "Mean Rating (excluding NAs)",
       y = "Proportion of Missing Ratings (NAs)") +
  theme_minimal()
```

OK so looks like NAs are positively correlated with values. Let's try looking at
Cronbach's alpha:
```{r include = FALSE}
library(dplyr)
library(tidyr)
library(psych)  # for alpha()

df_wide <- alldata[,c("participant","run","Q3_1","Q3_2","Q3_3")]
```

baseline alpha
```{r warning = FALSE}
alpha_results_list <- list()  # use a list instead of a tibble

  for (val in 0:9) {
    this_df <- df_wide %>%
      dplyr::mutate(across(-participant, ~ifelse(is.na(.), val, .)))
    alpha_val <- psych::alpha(this_df %>% select(-participant, -run), check.keys = TRUE)$total$raw_alpha
    alpha_results_list <- bind_rows(alpha_results_list,
                               tibble(imputed_value = val, alpha = alpha_val))
}

```
View the list
```{r warning = FALSE}
print(alpha_results_list)
```

Alpha is quite high no matter what, but definitely highest when NAs are imputed at zero.
```{r warning = FALSE}
ggplot(alpha_results_list, aes(x = imputed_value, y = alpha)) +
  geom_line(color = "steelblue", linewidth = 1.2) +
  geom_point(size = 2) +
  labs(
    title = "Cronbach’s Alpha by Imputed Value (0–9)",
    x = "Value Imputed for NAs",
    y = "Cronbach’s Alpha"
  ) +
  theme_minimal()
```
